
\smallskip
\cvevent{\large MENTOR}{Summer of Code in Space, ESA}{July 2019}{}
\begin{itemize}
\item Assigned as lead project mentor for a sub-project within the EinsteinPy project.
%\smallskip
\end{itemize}

\smallskip
\cvevent{\large DELEGATE}{Indian Youth Delegation to China}{July 2018}{}
\begin{itemize}
\item Represented India as a delegate in Indian Youth Delegation to China - 2018.
%\smallskip
\end{itemize}



\cvsection{\Large EDUCATION}
\cvevent{B.Tech (Electrical Engineering)}{Indian Institute of Technology, Mandi}{2016-2020}{Mandi}
\begin{itemize}
    \item CGPA: 7.61/10
\end{itemize}

\divider

\cvevent{CBSE (Matriculation \& Higher Secondary)}{D.A.V Public School}{2016}{Shrestha Vihar, Delhi}
\begin{itemize}
    \item X - 10/10 (CGPA)
    \item XII - 94.4\%
\end{itemize}


\smallskip
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{\Large Projects}


\cvproject{\href{https://github.com/einsteinpy/einsteinpy}{The EinsteinPy Project}}
\begin{itemize}
\item Founder of EinsteinPy - A Python library for General Relativity.
\item Partly sponsored by ESA(European Space Agency), OpenAstronomy and Google.
\end{itemize}
\smallskip

\cvproject{\href{https://github.com/ritzvik/ETHERNITY-CertificationOnBlockChain}{Certification on Blockchain}}
\begin{itemize}
    \item Designed and implemented a basic certification platform on ethereum smart contracts.
    \item Won 3rd prize in Topcoder Hackathon on the basis of this project.
\end{itemize}
\smallskip


\cvsection{\Large PUBLICATIONS}

\smallskip
\begin{itemize}
\item K. Agrawal, Y. Baweja, D. Dwivedi, R. Saha et al., "A Comparison of Class Imbalance Techniques for Real-World Landslide Predictions", in 2017 International Conference on Machine Learning and Data Science (MLDS), DOI 10.1109/MLDS.2017.21. Published by IEEE.
%\smallskip
\end{itemize}
