%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ritwik Saha} % Your name
\address{Mandi, Himachal Pradesh} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+91)~7838958076 \\ b16110@students.iitmandi.ac.in \\ www.linkedin.com/in/ritwik-saha \\ github.com/ritzvik} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Technology(Electrical Engineering)} \hfill {\em 2016 - 2020} 
\\ Indian Institute of Technology, Mandi \hfill { Overall GPA: 7.7/10}
\\ School of Computing and Electrical Engineering

\smallskip

{\bf CBSE(Higer Secondary)} \hfill {\em 2016} 
\\ D.A.V. Public School, Shreshtha Vihar, Delhi \hfill { Percentage: 94.4\%}

\smallskip

{\bf CBSE(Matriculation)} \hfill {\em 2014} 
\\ D.A.V. Public School, Shreshtha Vihar, Delhi \hfill { CGPA: 10.0}

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages &  C/C++, Python, MATLAB \\
Deep Learning Frameworks & Keras, TensorFlow \\
Containerization \& Orchestration & Docker, Kubernetes, KNative \\
IoT & Arduino, RaspberryPi \\
Graph Databases & Neo4J, ArangoDB \\
Blockchain & Ethereum, Solidity, Web3 \\

\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Siemens Technology \& Services Pvt. Ltd.}{June 2019 - August 2019}{Research Intern}{}
\item Set up infrastructure for running serverless applications.
\item Leveraged Docker, Kubernetes and KNative for setting up along with various network management framework like Istio.
\item Benchmarked the performance of the serverless setup under various load conditions and network topology.
\item Documented the relevant code and procedures. 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Siemens Technology \& Services Pvt. Ltd.}{December 2018 - Febraury 2019}{Research Intern}{}
\item Set up blockchain infrastructure with help of Private Ethereum.
\item Benchmarked the transaction performance, system resource usage and network performance under a variety of conditions like variable block times, transaction loads, block size etc.
\item Designed and partly implemented a supply chain solution on blockchain infrastructure.
\item Tried out and partially benchmarked various competing solutions for blockchain like Tendermint
\item Documented the relevant codebase and procedures.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Indian Institute of Technology, Mandi}{December 2018 - Febraury 2019}{Research Intern}{}
\item Set up blockchain infrastructure with help of Private Ethereum.
\item Benchmarked the transaction performance, system resource usage and network performance under a variety of conditions like variable block times, transaction loads, block size etc.
\item Designed and partly implemented a supply chain solution on blockchain infrastructure.
\item Tried out and partially benchmarked various competing solutions for blockchain like Tendermint
\item Documented the relevant codebase and procedures.
\end{rSubsection}

\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Achievements} \itemsep -2pt
\item Ranked in National Top 0.2\% (amongst 1,200,000 candidates) in JEE Mains 2013 and Top 1\% (amongst 150,000 candidates) in IIT-JEE Advanced 2013
\item Ranked in the State-wise Top 1\% (amongst 70,000 candidates) in State level Engineering competitive Exam (MP PET)
\item Stood first in MBD Talent Search Exam conducted by state government, competing against more than 1000 participants  
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Relevant Courses}
\itab{\textbf{Core Courses}} \tab{}  \tab{\textbf{Other Courses}}
\\ \itab{Fluid Mechanics \& its applications } \tab{}  \tab{Computational Methods in Engineering}
\\ \itab{Thermodynamics} \tab{}  \tab{Fundamental of Computing} 
\\ \itab{Heat Transfer \& its applications} \tab{}  \tab{Probability and Statistics} 
\\ \itab{Mass Transfer \& its applications} \tab{} \tab{Calculus \& Linear Algebra}
\\ \itab{Transport Phenomena (ongoing)} \tab{} \tab{Introduction to Mechanics}
% \\ \itab{Process Control (ongoing)} \tab{} \tab{Electrodynamics}

\end{rSection}

\begin{rSection}{POSITION OF RESPONSIBILITY}

\begin{rSubsection}{Techkriti 2015 - Technical and entrepreneurial Festival }{August 2014 - March 2015}{Public Relations}{IIT Kanpur}
\item Spearheaded a 2-tier team of 40 people to successfully conduct professional shows, exhibitions and talks
\item Organized talks in Techkriti by eminent personalities like Dr K. Radhakrishnan (Chairman, ISRO), Peter Schultz (Co-inventor, Fibre optics) and David Hilmers (NASA Astronaut) with more than 1000 attendees
\item Successfully organized Auto expo, Space expo and Defence expo together for the first time in Techkriti
\item Promoted awareness through social campaigns like Make a wish, Adopt a tree and Teen Suicide Prevention
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Students' Placement Office}{April 2015 - Present}{Internship Coordinator}{IIT Kanpur}
\item Coordinating with team of 20 students responsible for facilitating internship proceedings of 650 students involving 150 companies
 \item Responsible for developing contacts with corporate recruitment teams of several firms for internship and placements 
 \item Organized sessions on Personality Development and Career Awareness by esteemed alumni for over 1600 students
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Hall Executive Committee }{April 2014 - Nov 2014}{Secretary}{IIT Kanpur}
\item Coordinated with 12 members to led a team of 200 students in inter hall technical, cultural and sports competition of institute 
\item Planned an annual budget of 2 lakhs for proper functioning of hostel with more than 400 residents
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Cirrucular} \itemsep -3pt
\item Secured Gold in M.P. State Throw Ball competition and represented district in State Hand Ball competition
\item Represented Institute in Udghosh’13 and secured second prize in Kho-Kho intramurals
\item Secured second prize in Dance Drama competition in Galaxy’14, inter hall cultural competition of IIT Kanpur
\item Won second prize in Electromania, circuit game designing competition in Takneek’13, inter hall technical festival of IIT Kanpur
 % \item Member, Athletics Team, IIT Kanpur. Attended Summer Sport Camp as a long jumper.
%\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
 %\item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
 %\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
 %\item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %

\end{rSection}

\end{document}
